VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-11-01 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
fixed bibliography

\noindent
Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$. How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral?\\

@@

\bibitem{laurent1884} H.~Laurent, (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} \textbf{3}, No 3 (1884), 240--252.

@@

%physical
\bibitem{nigmatullin92} R.R.~Nigmatullin. A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} \textbf{90}, No 3 (1992): 242--251.

@@

\bibitem{ross06} B.Ross, (Ed.). \textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, \textbf{457}, Springer (1974).

>>>>

\noindent
Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Assume that $\widetilde{g}(x)$ is a differentiable and invertible real-valued function on $[a',b']$. How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral?\\

@@

\bibitem{laurent1884} H.~Laurent. Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} \textbf{3}, No 3 (1884), 240--252.

@@

%physical
\bibitem{nigmatullin92} R.R.~Nigmatullin. A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} \textbf{90}, No 3 (1992), 242--251.

@@

\bibitem{ross06} B.Ross, (Ed.). \textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}. \textbf{457}, Springer (1974).
